\LARGE \bf Efficient Sampling for Grasp Quality Evaluation on Gaussian Process Implicit Surface Representations [v-12 09-30-2014]

### 2014-10-01 paper.tex
changed section V

 To sample from $p(g)$, we need to compute the distributions associated with a line of action $p(n_i|c_i)p(c_i|\gamma_i(t),\mu(x),\Sigma(x))$ on each of the parameters: contact points $c_i$, surface normals $n_i$  and expected center of mass $\bar{z}$. 
 .
\subsection{Distribution on Contact Points} 
The probability distribution along the line $\gamma(t)$ is given by:

@@

This gives the signed distance function distributions along the entire line of action in the workspace as a multivariate Gaussian. One could think of this as a marginalization of all other points in signed distance field except the line of action. We would like to find the distribution on the first contact point, which we can define as when the signed distance function $sd(\gamma(t))$ is $0$ and all previous times $\tau$ we have $sd(\gamma(\tau)) > 0$ for all $\tau$ such that $0 \leq \tau < t$.We thus compute this as the joint distribution $p\big( \textbf{c}_i= \gamma(t)\big) = p\big(sd(\gamma(t))=0, sd(\gamma(\tau))> 0 \big)$ $  \forall \tau \in [0,t)$.

@@

\subsection{Distribution on Surface Normals} 
Using Eq. \ref{eq:mean_gradient} and Eq. \ref{eq:cov_gradient}, we can compute the mean of the gradient $ \mu_{\nabla}(x)$ and the covariance of the gradient $\Sigma_{\nabla}(x)$ respectively. Thus we can compute the distribution around the surface normal for a given point in $\mathcal{W}$. We can now write

@@

\subsection{Expected Center of Mass}

>>>>

 To sample from $p(g)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\mu(x),\Sigma(x))$. Using Bayes rule we can rewrite this as

 \vspace{-2ex}
 \begin{align*}
 &p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\mu(x),\Sigma(x))=\\
 &p(\textbf{n}_i|\textbf{c}_i,\gamma_i(t),\mu(x),\Sigma(x))p(c_i|\gamma_i(t),\mu(x),\Sigma(x))
 \end{align*}

 In section \ref{sec:contact}, we look at how to sample from $p(\textbf{c}_i|\gamma_i(t),\mu(x),\Sigma(x))$. Then in section \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\gamma_i(t),\mu(x),\Sigma(x))$ and present a novel visualization technique for the distribution on surface normals. Lastly in section \ref{sec:mass}, we show a way to calculate the expected center of mass assuming a uniform mass distribution. 
 .
\subsection{Distribution on Contact Points}\label{sec:contact} 
We would like to find the distribution on contact point $\textbf{c}_i$. A contact point in terms of the GPIS and line of action model can be defined as the point, $t$, when the signed distance function is zero and no points before said point along the line have touched the surface. We express this as the following conditions \\

\begin{enumerate}
	\item $sd(\gamma(t)) = 0$
	\item $sd(\gamma(\tau)) > 0$ $\forall \tau \in [a,t)$
\end{enumerate}

We now formally derive the distribution on contact point $p(\textbf{c}_i)$ using these conditions.  
. 
The probability distribution along the line $\gamma(t)$ is given by:

@@

This gives the signed distance function distributions along the entire line of action in the workspace as a multivariate Gaussian. One could think of this as a marginalization of all other points in signed distance field except the line of action. We would like to find the distribution on contact point $\textbf{c}_i$, which we can define as when the signed distance function $sd(\gamma(t))$ is $0$ and all previous times $\tau$ we have $sd(\gamma(\tau)) > 0$ for all $\tau$ such that $0 \leq \tau < t$.We thus compute this as the joint distribution $p\big( \textbf{c}_i= \gamma(t)\big) = p\big(sd(\gamma(t))=0, sd(\gamma(\tau))> 0 \big)$ $  \forall \tau \in [0,t)$.

@@

\subsection{Distribution on Surface Normals}\label{sec:normals} 
Using Eq. \ref{eq:mean_gradient} and Eq. \ref{eq:cov_gradient}, we can compute the mean of the gradient $ \mu_{\nabla}(x)$ and the covariance of the gradient $\Sigma_{\nabla}(x)$ respectively. Thus we can compute the distribution around the surface normal for a given point in $\mathcal{W}$. We can now write

@@

\subsection{Expected Center of Mass}\label{sec:mass}
